## Initial project scope
- Question
Where did e-scooter accidents happen more often in 2023?

- Hypothesis
E-scooter accidents more happened in the inner London than the outer London in 2023.
Null Hypothesis = no difference

- Analysis
Examine whether the results of the test confirm your hypothesis


```{r}
#load the libraries
library(sf)
library(here)
library(readr)
library(dplyr)
library(janitor)
library(tmap)
```

## Data loading
1)Road Safety Data - Vehicles 2023:<https://data.dft.gov.uk/road-accidents-safety-data/dft-road-casualty-statistics-vehicle-2023.csv>
vehicle_type:22 represents Mobility scooter
2)Road Safety Data - Collisions 2023:<https://data.dft.gov.uk/road-accidents-safety-data/dft-road-casualty-statistics-collision-2023.csv>
accident_index:join the Vehicles and Casualties data
longitude
latitude
3) Road Safety Data - Casualties 2023: <https://data.dft.gov.uk/road-accidents-safety-data/dft-road-casualty-statistics-casualty-2023.csv>
4)statistical-gis-boundaries-london.zip <https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip>

```{r}
#read the data
vehicles <- read_csv('https://data.dft.gov.uk/road-accidents-safety-data/dft-road-casualty-statistics-vehicle-2023.csv')
collisions <- read_csv('https://data.dft.gov.uk/road-accidents-safety-data/dft-road-casualty-statistics-collision-2023.csv')
casualties <- read_csv('https://data.dft.gov.uk/road-accidents-safety-data/dft-road-casualty-statistics-casualty-2023.csv')

Londonborough <- st_read(here::here('final exam','statistical-gis-boundaries-london','ESRI','London_Borough_Excluding_MHW.shp'))#WGS84

head(vehicles)
```
```{r}
# check the columns type
library(purrr)
Datatypelist <- tibble(variable = names(vehicles), # 提取列名
                         type = map_chr(vehicles,class) # 获取每列数据的底层类型
)
print(Datatypelist)
```



## Data wrangling
1) 选择事故车辆是e-scooter，并结合collision数据增加latitude and longitude
```{r}
#select the e-scooter accidents
e_scooter_accidents <- vehicles%>%
  clean_names()%>%
  filter(vehicle_type == 22)%>%#列名不需要quotes
  select(accident_index,vehicle_type)

#add the latitude and longitude
collisions_e_scooter <- left_join(e_scooter_accidents,collisions, by = NULL)
collisions_e_scooter_casualties <- left_join(collisions_e_scooter,casualties, by = NULL)
```
2)change the CRS
```{r}
#转换成sf
points_escooter <- collisions_e_scooter_casualties%>%
  st_as_sf(coords = c("longitude", "latitude"), 
                   crs = 4326)%>%
  st_transform(.,27700)

Londonborough <- Londonborough%>%
  clean_names()%>%
  st_transform(.,27700)
```

3)count the accidents by the districts
```{r}
points_escooter_Lon <- points_escooter[Londonborough,]

tmap_mode('plot')
tm_shape(Londonborough)+
  tm_polygons(col= "ons_inner",  # 按 one_inner 列上色
              palette =c("FALSE" = "#fde0dd", "TRUE" = "#c51b8a"),
              alpha=0.3)+
tm_shape(points_escooter_Lon)+
  tm_dots(col='blue')
```

## Data Analysis
### Ripley’s K-见practical6.6

