# Detecting spatial patterns

> how to begin to analyse patterns in spatial data Point Pattern Analysis

## Research Question

-   the patterns of Blue Plaques
-   For any given London Borough, are the Blue Plaques within that borough distributed randomly or do they exhibit some kind of dispersed or clustered pattern?”

## data exploration

### initial project scope

### packages

```{r}
#first library a few packages that we will use during the practical
#note you may need to install them first...
#install.packages("spatstat")
library(spatstat)
library(here)
library(sp)
library(tmap)
library(sf)
library(tmaptools)
library(stringr)
```

### Download the suggested datasets

read the data of London borough

```{r}
# 从 URL 下载和读取
url <- "https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip"
temp <- tempfile(fileext = ".zip")
download.file(url, temp)

# 解压文件
unzip(temp, exdir = tempdir())

#并找到 .shp 文件路径
shp_file <- list.files(tempdir(), pattern = "\\.shp$", full.names = TRUE, recursive = TRUE)
# 检查是否找到 .shp 文件
if (length(shp_file) == 0) {
  stop("没有找到 .shp 文件，请检查 URL 或解压目录。")
}

# 读取 .shp 文件
LondonBoroughs <- st_read(shp_file[19])%>%
  st_transform(., 27700)

```

**加载动态底图？**

```{r}
qtm(LondonBoroughs)
```

```{r}
summary(LondonBoroughs)
```

-   load the data of Blue Plaques

```{r}
##Now get the location of all Blue Plaques in the City
BluePlaques <- st_read("https://s3.eu-west-2.amazonaws.com/openplaques/open-plaques-london-2018-04-08.geojson")

summary(BluePlaques)

```

-   Finding: the CRS of BluePlaques is 4326, different from that of LondonBoroughs.

```{r}
#change the CRS
BluePlaques <- BluePlaques %>%
  st_transform(., 27700)
summary(BluePlaques)
```

```{r}
#plot the blue plaques in the city
tmap_mode("plot")
tm_shape(LondonBoroughs) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaques) +
  tm_dots(col = "blue")
```

## Analysis

### Data cleaning

Due to the error locations of some blue plaques, my first step is to remove the special points outside of the Borough boundaries.

```{r}
#remove duplicates
library(tidyverse)

library(sf)
BluePlaques <- distinct(BluePlaques)
```

### Spatial subsetting

拓扑关系 -\> Spatial clipping - Spatial clipping \> st union(x, y) \> st difference(x, y) \> st intersection(x, y) \> st difference(y, x) \> st sym difference(x, y) **不同拓扑关系的函数** <https://postgis.net/workshops/postgis-intro/spatial_relationships.html>

```{r}
BluePlaquesSub <- BluePlaques[LondonBoroughs,]

#or将运算符或 op 设置为st_within ，以识别完全在行政区轮廓内的点
#BluePlaquesSub <- BluePlaques[BoroughMap, , op = st_within]

#check to see that they've been removed
tmap_mode("plot")
tm_shape(LondonBoroughs) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaquesSub) +
  tm_dots(col = "blue")
```

use the function which will have the indices of where they intersect

```{r}
# add sparse=false to get the complete matrix.
intersect_indices <-st_intersects(LondonBoroughs,
                                  BluePlaques,
                                  sparse = FALSE) # sparse=false 获取完整的相交矩阵
```

\-`ST_Intersects` & `ST_Within` st_within 不会选择不完全位于多边形内的线。

### Spatial joining

```{r}
#读取osm(.shp)
url_OSM <- "https://download.geofabrik.de/europe/united-kingdom/england/greater-london-latest-free.shp.zip"
temp_OSM <- tempfile(fileext = ".zip")
download.file(url_OSM, temp_OSM)
unzip(temp_OSM, exdir = tempdir())
shp_file_OSM <- list.files(tempdir(), pattern = "\\.shp$", full.names = TRUE, recursive = TRUE)

OSM <- st_read(shp_file_OSM[9]) %>%
  st_transform(., 27700)
```
