<<<<<<< HEAD
### Load Package

```{r}
library(sf)
library(jsonlite)
library(tmap)
library(tmaptools)
library(tidyverse)
library(here)

```

### read the raw data

-   本地加载文件，无法将数据上传GitHub的repo，文件太大.

```{r}
`Londonborough <- st_read(here::here("wk5_data",                                "statistical-gis-boundaries-london",   
"ESRI",                                     
"London_Borough_Excluding_MHW.shp"))%>%   st_transform(., 27700)`
```

-   利用url链接加载.shp文件\

```{r}
# 从 URL 下载和读取
url <- "https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip"
temp <- tempfile(fileext = ".zip")
download.file(url, temp)

# 解压文件
unzip(temp, exdir = tempdir())

#并找到 .shp 文件路径
shp_file <- list.files(tempdir(), pattern = "\\.shp$", full.names = TRUE, recursive = TRUE)
# 检查是否找到 .shp 文件
if (length(shp_file) == 0) {
  stop("没有找到 .shp 文件，请检查 URL 或解压目录。")
}

# 读取 .shp 文件
Londonborough <- st_read(shp_file[34])%>%
  st_transform(., 27700)

```

```{r}
#读取osm(.shp)
url_OSM <- "https://download.geofabrik.de/europe/united-kingdom/england/greater-london-latest-free.shp.zip"
temp_OSM <- tempfile(fileext = ".zip")
download.file(url_OSM, temp_OSM)
unzip(temp_OSM, exdir = tempdir())
shp_file_OSM <- list.files(tempdir(), pattern = "\\.shp$", full.names = TRUE, recursive = TRUE)

OSM <- st_read(shp_file_OSM[9]) %>%
  st_transform(., 27700) %>%
  #select hotels only
  dplyr::filter(fclass == 'hotel')
```

\-`fromjson`读取的数据通常是普通的 JSON 格式，无法直接使用 `sf` 函数进行空间操作。

```{r}
#读取Worldcities(.GeoJSON)
Worldcities <- st_read(here::here("wk5/practical5_data",
                                  "World_Cities.geojson") )%>%
  st_transform(., 27700) 

Worldcities2 <- Worldcities %>%
  filter(CNTRY_NAME=='United Kingdom'&
           Worldcities$CITY_NAME=='Birmingham'|
           Worldcities$CITY_NAME=='London'|
           Worldcities$CITY_NAME=='Edinburgh')
=======
```


```{r}
#读取uk_outline(.shp)
url_UK <- "https://geodata.ucdavis.edu/gadm/gadm4.1/shp/gadm41_GBR_shp.zip"
temp_UK <- tempfile(fileext = ".zip")
download.file(url_UK, temp_UK)
unzip(temp_UK, exdir = tempdir())
shp_file_UK <- list.files(tempdir(), pattern = "\\.shp$", full.names = TRUE, recursive = TRUE)

UK_outline <- st_read(shp_file_UK[1]) %>%
  st_transform(., 27700)
```

```{r}
=======

>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
#定义边界框坐标
newbb <- c(xmin=-296000, ymin=5408, xmax=655696, ymax=1000000)
  
UK_outlinecrop <- UK_outline$geometry %>%
  st_crop(., newbb)
```
<<<<<<< HEAD

=======
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
join_example <-  st_join(Londonborough, OSM)

head(join_example)
```
<<<<<<< HEAD

-  读取airbnb数据

=======
- 读取airbnb数据
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
# read in the .csv
# and make it into spatial data

Airbnb <- read_csv("wk7_data/listings.csv") %>%
  # longitude is considered x value here, latitude is y
  st_as_sf(., coords = c("longitude", "latitude"), 
                   crs = 4326) %>%
    st_transform(., 27700)%>%
    #select entire places that are available all year
    filter(room_type == 'Entire home/apt' & availability_365 =='365')


```

设置一个函数用于连接
<<<<<<< HEAD

=======
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
# make a function for the join
# functions are covered in practical 7
# but see if you can work out what is going on
# hint all you have to do is replace data1 and data2
# with the data you want to use

Joinfun <- function(data1, data2){

output<- data1%>%
  st_join(data2,.) %>%
  add_count(GSS_CODE, name="hotels_in_borough") 

  return(output)
}

# use the function for hotels
Hotels <- Joinfun(OSM, Londonborough)

# then for airbnb
# this is incorrect - change to airbnb2 to look at result
Airbnb <- Joinfun(Airbnb, Londonborough)

Hotels <- Hotels %>%
  #at the moment each hotel is a row for the borough
  #we just one one row that has number of airbnbs
  group_by(., GSS_CODE, NAME)%>%
  summarise(`Accomodation count` = unique(hotels_in_borough))

Airbnb <- Airbnb %>%
  group_by(., GSS_CODE, NAME)%>%
  summarise(`Accomodation count` = unique(hotels_in_borough))
```
<<<<<<< HEAD

问题：如何排除空集？

=======
问题：如何排除空集？
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
Airbnb %>%
  filter(NAME=="Sutton")
```

制作地图
<<<<<<< HEAD

=======
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
tmap_mode("plot")

# set the breaks
# for our mapped data
breaks = c(0, 5, 12, 26, 57, 286) 

# plot each map
tm1 <- tm_shape(Hotels) + 
  tm_polygons("Accomodation count", 
              breaks=breaks,
              palette="PuBu")+
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(a)", position=c(0,0.85), size=1.5)

tm2 <- tm_shape(Airbnb) + 
  tm_polygons("Accomodation count",
              breaks=breaks, 
              palette="PuBu") + 
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(b)", position=c(0,0.85), size=1.5)

tm3 <- tm_shape(UK_outlinecrop)+ 
  tm_polygons(col="darkslategray1")+
  tm_layout(frame=FALSE)+
  tm_shape(Worldcities2) +
  tm_symbols(col = "red", scale = .5)+
  tm_text("CITY_NAME", xmod=-1, ymod=-0.5)

legend <- tm_shape(Hotels) +
    tm_polygons("Accomodation count",
                breaks=breaks,
                palette="PuBu") +
    tm_scale_bar(position=c(0.2,0.04), text.size=0.6)+
    tm_compass(north=0, position=c(0.65,0.6))+
    tm_layout(legend.only = TRUE, legend.position=c(0.2,0.25),asp=0.1)+
    tm_credits("(c) OpenStreetMap contrbutors and Air b n b", position=c(0.0,0.0))
  
t=tmap_arrange(tm1, tm2, tm3, legend, ncol=2)

t
```

```{r}
library(grid)
# erases the current device or moves to a new page 
# probably not needed but makes sure you are plotting on a new page.
grid.newpage()

pushViewport(viewport(layout=grid.layout(2,2)))
print(tm1, vp=viewport(layout.pos.col=1, layout.pos.row=1, height=5))
print(tm2, vp=viewport(layout.pos.col=2, layout.pos.row=1, height=5))
print(tm3, vp=viewport(layout.pos.col=1, layout.pos.row=2, height=5))
print(legend, vp=viewport(layout.pos.col=2, layout.pos.row=2, height=5))
```
<<<<<<< HEAD

嵌套地图

=======
嵌套地图
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
Londonbb <- st_bbox(Airbnb,
                    crs = st_crs(Airbnb))%>%
  #we need this to convert it into a class of sf
  # otherwise it our bb won't have a class it will just be x and y coordinates for the box
  # this makes it into a polygon
  st_as_sfc()
```

```{r}
main <- tm_shape(Airbnb, bbbox = Londonbb) + 
  tm_polygons("Accomodation count",
              breaks=breaks, 
              palette="PuBu")+
  tm_scale_bar(position = c("left", "bottom"), text.size = .75)+
  tm_layout(legend.position = c("right","top"), 
            legend.text.size=.75, 
            legend.title.size = 1.1,
            frame=FALSE)+
  tm_credits("(c) OpenStreetMap contrbutors and Air b n b", position=c(0.0,0.0))+
  #tm_text(text = "NAME", size = .5, along.lines =T, remove.overlap=T,  auto.placement=F)+
  tm_compass(type = "8star", position = c(0.06, 0.1)) +

  #bottom left top right
  tm_layout(inner.margin=c(0.02,0.02,0.02,0.2))
```

```{r}
inset = tm_shape(UK_outlinecrop) + tm_polygons() +
  tm_shape(Londonbb)+ 
  tm_borders(col = "grey40", lwd = 3)+
    tm_layout(frame=FALSE,
            bg.color = "transparent")+
  tm_shape(Worldcities2) +
  tm_symbols(col = "red", scale = .5)+
  tm_text("CITY_NAME", xmod=-1.5, ymod=-0.5)
```

```{r}
library(grid)
main
print(inset, vp = viewport(0.86, 0.29, width = 0.5, height = 0.55))
```

输出地图
<<<<<<< HEAD

=======
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
tmap_save(t, 'hotelsandairbnbR.png')

library(grid)
tmap_save(main,insets_tm = inset,insets_vp=viewport(x=0.86, y=0.29, width=.5, height=.55), filename="test.pdf", dpi=600)
```

交互地图
<<<<<<< HEAD

=======
>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
```{r}
tmap_mode("view")

tm_shape(Airbnb) + 
  tm_polygons("Accomodation count", breaks=breaks) 
```
<<<<<<< HEAD
=======


>>>>>>> eb0bdd1c3f3fd32255c67f23dee0ea30be34413e
